\section{Dataset}
\label{sec:dataset}

\subsection{Frameworks}

We ingest 12 AI security frameworks spanning governance, technical
controls, and threat modeling:
NIST AI RMF, NIST SP~800-53, MITRE ATLAS, OWASP LLM Top~10,
OWASP ML Top~10, ISO/IEC~42001, EU AI Act, AISI Inspect,
CSA AI Controls Matrix, MAESTRO, Google SAIF, and the OWASP AI
Exchange. Together these yield 983 control nodes.

\subsection{Graph Structure}

The control graph contains 6{,}383 edges from three sources:
(1)~within-framework parent--child hierarchies,
(2)~cross-framework prior edges from the GenAI Security Project
crosswalk (CC~BY-SA~4.0), and
(3)~algorithmically generated bridge edges from high-confidence
BM25 matches. The graph spans 26 framework pairs.

\subsection{Labeling Protocol}

We employ a two-stage labeling protocol:
\begin{enumerate}
    \item \textbf{LLM-SME silver labels.} A structured prompt elicits
          tier judgments from a large language model acting as a
          simulated subject matter expert. Each pair receives a tier
          label (0--3) and a free-text rationale. 1{,}515 training pairs
          and 379 validation pairs are labeled this way.
    \item \textbf{Expert gold labels.} A human expert independently
          labels 400 pairs using the same 4-tier scheme. These form
          the frozen test set (\texttt{v1\_frozen}) used for all
          reported metrics. The frozen split is SHA-verified and never
          used during training or hyperparameter selection.
\end{enumerate}

\subsection{Tier Scheme}

The four tiers capture decreasing degrees of semantic overlap:
\begin{description}
    \item[Equivalent (3):] Controls address the same requirement with
          comparable specificity.
    \item[Related (2):] Controls address overlapping concerns but differ
          in scope or granularity.
    \item[Partial (1):] One control partially addresses the other's
          requirement.
    \item[Unrelated (0):] No meaningful semantic overlap.
\end{description}
