\section{Experimental Setup}
\label{sec:experiments}

\subsection{Feature Set}

The full feature vector comprises 38 dimensions:
\begin{itemize}
    \item \textbf{Text features:} BGE-large cosine similarity,
          BM25 score, Jaccard coefficient, character n-gram overlap.
    \item \textbf{Graph features:} GATv2 cosine similarity, GATv2 L2
          distance, element-wise product pooling, bridge centrality,
          shortest-path distance, common-neighbor count.
    \item \textbf{Metadata features:} same-framework indicator,
          framework-pair one-hot encoding, control depth difference.
\end{itemize}

\subsection{Training Configuration}

\begin{itemize}
    \item \textbf{Classifier:} LightGBM multiclass (softmax objective).
    \item \textbf{Class weights:} Inverse-frequency weighting to
          compensate for severe imbalance (the unrelated class dominates
          at $>$60\% of pairs).
    \item \textbf{Hyperparameter search:} Optuna with 200 trials,
          optimizing macro F1 on 5-fold cross-validation over the
          training split.
    \item \textbf{Training data:} 1{,}515 LLM-SME labeled pairs.
    \item \textbf{Validation data:} 379 LLM-SME labeled pairs.
    \item \textbf{Test data:} 400 expert-labeled frozen pairs
          (\texttt{v1\_frozen}), never seen during training or tuning.
\end{itemize}

\subsection{Evaluation Metrics}

We report tier accuracy (exact match), macro F1, per-class precision
and recall, and conformal coverage at $\alpha=0.10$. All confidence
intervals are computed via 10{,}000-iteration bootstrap resampling.
