\section{Introduction}
\label{sec:intro}

The rapid proliferation of AI security frameworks has created a
compliance landscape in which organizations must simultaneously satisfy
multiple overlapping standards. Frameworks such as the NIST AI Risk
Management Framework~\citep{nist_ai_rmf}, MITRE
ATLAS~\citep{mitre_atlas}, the OWASP Top~10 for LLM
Applications~\citep{owasp_llm_top10}, and the CSA AI Controls
Matrix~\citep{csa_aicm} each use their own taxonomy, control
identifiers, and terminology, making it difficult for practitioners to
determine which controls in one framework correspond to controls in
another.

Manual crosswalk construction is the current industry practice. Subject
matter experts review pairs of controls across frameworks and assign
equivalence judgments. This process is slow (a single multi-framework
crosswalk can take hundreds of hours), subjective (inter-annotator
agreement is often low for partial-overlap cases), and brittle (each
framework revision invalidates portions of the mapping).

We propose an automated crosswalk system that scales to arbitrary
framework pairs. Our pipeline ingests framework control texts, builds a
multi-framework knowledge graph from four complementary data sources,
and trains a supervised classifier to assign one of four relationship
tiers to each candidate control pair. The system incorporates three
signal families: (1)~LLM-derived semantic similarity features,
(2)~structural graph features from the control knowledge graph, and
(3)~calibrated LLM-as-judge tier scores from a Claude Opus evaluator.

A Mondrian conformal prediction wrapper provides finite-sample coverage
guarantees per class, and a KL-divergence router identifies predictions
where the model is uncertain, routing them to human reviewers. The
result is a human-in-the-loop system that automates the bulk of
crosswalk construction while preserving expert oversight where it
matters most.

We evaluate on 400 expert-labeled frozen test pairs spanning 15
framework pairs across nine AI security and governance frameworks,
achieving tier accuracy of 0.53 with a bootstrap 95\% confidence
interval of [0.485, 0.580] and macro F1 of 0.49. Adjacent accuracy
(predictions within one tier of ground truth) reaches 0.84, and
Mondrian conformal prediction achieves 93.8\% empirical coverage at
$\alpha = 0.10$.
