\section{Method}
\label{sec:method}

Our pipeline comprises four stages: feature extraction, graph learning,
stacking classification, and uncertainty quantification.

\subsection{Text Embeddings}

For each control node we compute two text representations:
\begin{itemize}
    \item \textbf{BGE-large} dense embeddings (1024-d), producing
          cosine similarity features for each candidate pair.
    \item \textbf{BM25} sparse lexical scores, computed over
          control titles and descriptions after standard tokenization
          and stopword removal.
\end{itemize}

\subsection{Graph Construction and GATv2}

We construct a heterogeneous control graph with 983 nodes (one per
control across all 12 frameworks) and 6{,}383 edges derived from
within-framework hierarchies, cross-framework prior edges from the
GenAI Security Project crosswalk, and high-confidence BM25 bridge edges.

A two-layer GATv2~\citep{brody2022gatv2} network is trained on this
graph using a link-prediction objective. The resulting node embeddings
(128-d) capture structural proximity: controls that are connected
through multiple paths in the graph receive similar representations
regardless of surface-level text overlap.

For each candidate pair $(u, v)$, we extract four GATv2-derived
features: cosine similarity of node embeddings, L2 distance, element-wise
product pooling, and a bridge centrality score.

\subsection{LightGBM Stacker}

All features---text similarity, graph structural, and metadata---are
concatenated into a 38-dimensional feature vector and fed to a
LightGBM~\citep{ke2017lightgbm} multiclass classifier. The model
predicts one of four tiers: \emph{unrelated} (0), \emph{partial} (1),
\emph{related} (2), and \emph{equivalent} (3). Inverse-frequency class
weights address the severe class imbalance. Hyperparameters are tuned
via Optuna with 5-fold cross-validation.

\subsection{Mondrian Conformal Prediction}

We wrap the LightGBM classifier with a Mondrian conformal predictor
that provides per-class coverage guarantees. For each test instance, the
conformal predictor outputs a prediction set guaranteed to contain the
true label with probability $\geq 1-\alpha$ within each class stratum.

\subsection{KL-Divergence Router}

A KL-divergence router compares the predicted class distribution against
a uniform reference distribution. Instances with high KL divergence
(confident predictions) are accepted; those with low divergence
(uncertain predictions) are routed to human review. This creates a
natural human-in-the-loop workflow where experts focus on the most
ambiguous cases.
