\section{Reproducibility}
\label{sec:reproducibility}

We prioritize full reproducibility of all reported results:

\begin{itemize}
    \item \textbf{One-command reproduction.} Running \texttt{make
          reproduce} verifies frozen-split integrity via SHA-256 hashes,
          re-evaluates the trained model on the frozen test set, and
          reports all metrics from Section~\ref{sec:results}.
    \item \textbf{Pinned dependencies.} All Python dependencies are
          pinned in \texttt{requirements.txt} with exact versions.
    \item \textbf{Frozen test splits.} The 400 expert-labeled test
          pairs are stored in
          \texttt{data/splits/human\_test\_frozen.jsonl} with a derived
          \texttt{frozen\_tuples.json} file. A SHA-256 hash verification
          contract test ensures these files are never inadvertently
          modified.
    \item \textbf{Sacred experiment tracking.} The canonical run
          (\texttt{v6-reframed}, SHA \texttt{3c2e531}) is logged with
          all hyperparameters, random seeds, feature definitions, and
          metric values recorded in
          \texttt{results/sacred/sacred\_3c2e531.json}.
    \item \textbf{Four-source data provenance.} All upstream data
          sources (community mappings, cross-references, and
          bootstrap-pruned anchor pairs) are versioned in the
          repository with their generation scripts.
    \item \textbf{Source code.} The complete codebase is released under
          the Apache-2.0 license.
\end{itemize}
